Stellar and Planetary Properties of \KT\ \Ci\ Candidates and Validation of \Nvalidated\ Systems, Including a Planet Receiving Earth-like Insolation

### 2015-03-12 ms.tex
more discussion

>>>>

The planets we confirm in this paper, like the planets found in the original \kep\ mission,
span a wide range of parameter space. 
They are at distances ranging from $34$ to $500$ pc, have radii ranging from $1.3$ to 
$5.3 R_\odot$, and orbital periods ranging from 5.0 to 50.3 days.
Like the original mission, we find significantly more small planets than large planets.

Unlike the original mission, however, we find that nearly all of our confirmed planets
are around stars less massive than the Sun. 
This difference is a result of both the \Ci\ field and the target selection process.
\Ci\ is at a significantly higher galactic latitude than the original \kep\ mission, 
meaning there is a much lower number density of targets at large distances.
A magnitude limited survey pointed in this direction would then have much in
common with a volume limited survey near the galactic plane, as massive stars
at kiloparsec distances are relatively unlikely likely to exist.
Therefore, the pool of targets that could be selected for \Ci\ contains a larger
fraction of subsolar stars.

Low-mass stars, particularly M dwarfs, are also a specific focus of the \KT\ mission.
One of the primary goals of the Kepler mission was to ``Determine the abundance of 
terrestrial and larger planets in or near the habitable zone of a wide variety of spectral 
types of stars'' \citep{Batalha13} However, $\sim70\%$ of Kepler's target stars had 
masses within 20\% 
of the Sun's, while 70\% of the stars in the Galaxy have less than 50\% the mass of the 
Sun \citep{Brown11}.
\KT\ will fulfill the promise of \kep, with the goal of providing a yield of small planets
around bright, small stars to facilitate follow-up measurements \citep{Howell14}.
This is clear from the \KT\ target selection process, with thousands of K and M dwarfs
being selected in each campaign.
Based on these plans, we expect that \KT\ will detect hundreds of planets during its 
lifetime, with the majority being mini-Neptunes and super-Earths around stars
less massive than the Sun.

\anytodo{Does anyone feel we should include anything else in the discussion?}
